\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{dirtree}

\include{defs}

\usepackage[english]{babel}
 

\usepackage{lipsum}

%%%%%%%%%%%%%%%
% Title Page
\title{Frond End Manual}
\author{Raghuvar Prajapati}
\date{\today}
%%%%%%%%%%%%%%%

\begin{document}
\maketitle

\tableofcontents
\clearpage

\section{Problem Statement}

\textbf{Design a Front End}\\

\textbf{Details:} 

\begin{itemize}
\item Implement the design from the following image: http://bit.ly/frontendimage
\item Make it responsive.
\item All files should be concatenated, minified or otherwise generally optimized.
\item Any image / text content can be used but the look and feel of the image needs to be captured.
\item Write an additional document with a structure of your submission directory and any instructions to build / run your code. The root structure we would recommend is:
Directory
--- dist (Concatentated and minified files) \\
--- index.html \\
--- [any build tool files] \\
--- src (Source files)
\end{itemize}

\section{Framework}
I have used Bootstrap framework to build the front end part.

\section{Instructions}
Please navigate to the main directory. I have run the code in Linux machine. \\
Directory Structure looks like:\\
--dist\\
--src\\
--index.heml



\newpage
\begin{itemize}
\item You will just have to run index.html page in your browser.
\item Can be run into your server custom folder.
\item In linux put the folder into /var/www/html.
\item Open your browser and go to localhost/$<$direc$_{-}$name$>$
\end{itemize}
\end{document}          
